Species motif participation provides unique information about species risk of extinction

### 2023-04-04 manuscript/reorder_main_text.tex
Updates from Overleaf

    \begin{figure}[hb!]
        \centering
        \includegraphics[width=\textwidth]{figures/persistence_motif_profiles.eps}
        \caption{The proportions of the four motifs in a network's motif profile are related to the mean persistence of species in the network. Specifically, persistence decreases as the proportion of omnivory in the network's motif profile increases while persistence increases with the proportions of the other three motifs. Interactions between motif profiles and disturbance were significant but small. Here we show the relationships of probabilities of extinction of basal resources of $\pi=0.1$ (top set of lines) and $\pi=0.5$ (bottom set of lines). Relationships are shown for the observed range of proportions for each motif.}      
        \label{fig:motif_profile_persistence}
    \end{figure}

    \begin{figure}[hb!]
        \centering
        \includegraphics[width=\textwidth]{figures/motif_proportion_lms.eps}
        \caption{The proportions of the four motifs in a network's motif profile were related to network size, connectance, and their interaction. The effect of connectance was much stronger than the main effect or interaction with network size. The proportion of apparent competition in a network's profile decreased with increasing connectance, while the proportion of omnivory increased. In small networks, the proportion of direct competition also decreased with increasing connectance.}
        \label{motif_proportion_lms}
    \end{figure}

>>>>

    \begin{figure}[hb!]
        \centering
        \includegraphics[width=\textwidth]{figures/persistence_motif_profiles.eps}
        \caption{The proportions of the four motifs in a network's motif profile are related to the mean persistence of species in the network. Specifically, persistence decreases as the proportion of omnivory in the network's motif profile increases while persistence increases with the proportion of the apparent competition motifs. Interactions between motif profiles and disturbance were not significant. Here we show the relationships of probabilities of extinction of basal resources of $\pi=0.1$ (top set of lines) and $\pi=0.5$ (bottom set of lines). Relationships are shown for the observed range of proportions for each motif.}      
        \label{fig:motif_profile_persistence}
    \end{figure}

    \begin{figure}[hb!]
        \centering
        \includegraphics[width=\textwidth]{figures/motif_proportion_lms.eps}
        \caption{The proportion of the omnivory in a network's motif role increased significantly as connectance increased, while the proportions of the other three motifs did not vary significantly with network size, connectance, or their interaction.}
        \label{motif_proportion_lms}
    \end{figure}
